### 2021-07-01 src/paper/literature_review.tex
Add comment on Twitter feedback on other agent based models.

Another commonly used model class in epidemiology are agent-based simulation models. In
these models individuals are simulated as moving particles. Infections take place when
two particles come closer than a certain contact radius (e.g. \citet{Silva2020} and
\citet{Cuevas2020}). While the simulation approach makes it easy to incorporate
heterogeneity in disease progression, it is hard to incorporate heterogeneity in meeting
patterns. Moreover, policies are modeled as changes in the contact radius or momentum
equation of the particles. The translation from real policies to corresponding model
parameters is a hard task.

>>>>

Another commonly used model class in epidemiology are agent-based simulation
models.\comment[id=K]{See
\href{https://twitter.com/Patrick_M_Econ/status/1410543606939721730?s=20}{this tweet} for
a reference to some models that are similar to ours} In these models individuals are
simulated as moving particles. Infections take place when two particles come closer than
a certain contact radius (e.g. \citet{Silva2020} and \citet{Cuevas2020}). While the
simulation approach makes it easy to incorporate heterogeneity in disease progression, it
is hard to incorporate heterogeneity in meeting patterns. Moreover, policies are modeled
as changes in the contact radius or momentum equation of the particles. The translation
from real policies to corresponding model parameters is a hard task.
